Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-02 paper/paper.tex
feature sections

\documentclass[11pt,letterpaper]{article}
\usepackage{naaclhlt2013}
\usepackage{times}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{paralist}
\defaultleftmargin{1em}{}{}{} % default is 2em

@@

\title{Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em]
{\large Chris Dyer$^1$ Manaal Faruqui$^1$ Noam Ordan$^2$ Nathan Schneider$^1$\\ Yulia Tsvetkov$^1$ Naama Twitto$^2$ Shuly Wintner$^2$}\\[-3em]
}

\author{
\\
$^1$Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
\And
\\
$^2$Department of Computer Science\\University of Haifa\\Haifa, Israel\\\texttt{shuly@cs.haifa.ac.il}
%
%
%C.\ Dyer M.\ Faruqui N.\ Schneider Y.\ Tsvetkov\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
%\And
%N.\ Ordan N.\ Twitto S.\ Wintner\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{shuly@cs.haifa.ac.il}
%
%
%Chris Dyer\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
%\And
%Manaal Faruqui\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{manaalfar@gmail.com}
%\And
%Noam Ordan\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{noam.ordan@gmail.com}
%\And
%Nathan Schneider\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{nathan@cmu.edu}
%\And
%Yulia Tsvetkov\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{yulia.tsvetkov@gmail.com}
%\And
%Naama Twitto\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{naama.twitto@gmail.com}
%\And
%Shuly Wintner\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{shuly@cs.haifa.ac.il}
}

@@

We address the task as a multiway text-classification task; we specify
our methodology in Section~\ref{sec:methodology}. As in other author
attribution tasks \citep{joula:2006}, the choice of features for the
classifier is crucial; we discuss the features we define in
Section~\ref{sec:features}. We report our results in
Section~\ref{sec:results} and conclude with suggestions for future
research.

@@

\section{Features}
\label{sec:features}
We define a large arsenal of features, our motivation being both to
improve the accuracy of classification and to be able to interpret the
characteristics of the language produced by speakers of different
L1s. In this section we define the features and motivate their use.%
\footnote{Whenever counts are mentioned, we use the log of the count
  as the feature.}  
While some of the features were used in the works surveyed in
Section~\ref{sec:literature}, many are novel, and are inspired by the
features used to identify translationese by \citet{vered:noam:shuly}.
We also report the accuracy of using each feature type, in isolation,
on the training set.

@@

>>>>

\documentclass[11pt,letterpaper]{article}
\usepackage[linkcolor=blue]{hyperref}	% must precede ACL style
\usepackage{relsize} % relative font sizes (e.g. \smaller). must precede ACL style
\usepackage{naaclhlt2013}
\usepackage{times}
\usepackage{latexsym}

\usepackage{amsmath,amsfonts,eucal,amsbsy,amsthm,amsopn,amssymb}

\usepackage{txfonts}
\usepackage[scaled]{beramono}
\usepackage[T1]{fontenc}

\usepackage{paralist}
\defaultleftmargin{1em}{}{}{} % default is 2em

@@

% Author comments
\usepackage{color}
\usepackage{bm}
\definecolor{orange}{rgb}{1,0.5,0}
\definecolor{mdgreen}{rgb}{0,0.6,0}
\definecolor{dkblue}{rgb}{0,0,0.5}
\definecolor{dkgray}{rgb}{0.3,0.3,0.3}
\definecolor{slate}{rgb}{0.25,0.25,0.4}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{purple}{rgb}{0.7,0,1.0}
\newcommand{\ensuretext}[1]{#1}
\newcommand{\cjdmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{CJ}}_{\textsc{D}}}}}}
\newcommand{\nssmarker}{\ensuretext{\textcolor{magenta}{\ensuremath{^{\textsc{NS}}_{\textsc{S}}}}}}
\newcommand{\swmarker}{\ensuretext{\textcolor{red}{\ensuremath{^{\textsc{S}}_{\textsc{W}}}}}}
\newcommand{\ytmarker}{\ensuretext{\textcolor{blue}{\ensuremath{^{\textsc{Y}}_{\textsc{T}}}}}}
\newcommand{\ntmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{N}}_{\textsc{T}}}}}}
\newcommand{\arkcomment}[3]{\ensuretext{\textcolor{#3}{[#1 #2]}}}
%\newcommand{\arkcomment}[3]{}
\newcommand{\cjd}[1]{\arkcomment{\cjdmarker}{#1}{green}}
\newcommand{\nss}[1]{\arkcomment{\nssmarker}{#1}{magenta}}
\newcommand{\sw}[1]{\arkcomment{\swmarker}{#1}{red}}
\newcommand{\yt}[1]{\arkcomment{\ytmarker}{#1}{blue}}
\newcommand{\nt}[1]{\arkcomment{\ntmarker}{#1}{orange}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\g}{\mathbf{g}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\x}{\boldsymbol{x}}
\newcommand{\y}{\boldsymbol{y}}
\newcommand{\cost}{c}

\newcommand{\Sref}[1]{\S\ref{#1}}
\newcommand{\fref}[1]{figure~\ref{#1}}
\newcommand{\Fref}[1]{Figure~\ref{#1}}
\newcommand{\tref}[1]{table~\ref{#1}}
\newcommand{\Tref}[1]{Table~\ref{#1}}

% special macros

\newcommand{\feat}[1]{\textsmaller[.5]{\textsf{#1}}} % code for a feature group

\title{Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em]
{\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]
}

\author{
\\
$^\ast$Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
\And
\\
$^\dagger$Department of Computer Science\\University of Haifa\\Haifa, Israel\\\texttt{shuly@cs.haifa.ac.il}
%
%
%C.\ Dyer M.\ Faruqui N.\ Schneider Y.\ Tsvetkov\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
%\And
%N.\ Ordan N.\ Twitto S.\ Wintner\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{shuly@cs.haifa.ac.il}
%
%
%Chris Dyer\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{cdyer@cs.cmu.edu}
%\And
%Manaal Faruqui\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{manaalfar@gmail.com}
%\And
%Noam Ordan\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{noam.ordan@gmail.com}
%\And
%Nathan Schneider\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{nathan@cmu.edu}
%\And
%Yulia Tsvetkov\\Language Technologies Institute\\Carnegie Mellon University\\Pittsburgh, PA\\\texttt{yulia.tsvetkov@gmail.com}
%\And
%Naama Twitto\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{naama.twitto@gmail.com}
%\And
%Shuly Wintner\\Department of Computer Science\\University of Haifa\\Israel\\\texttt{shuly@cs.haifa.ac.il}
}

@@

We address the task as a multiway text-classification task; we specify
our methodology in \Sref{sec:methodology}. As in other author
attribution tasks \citep{joula:2006}, the choice of features for the
classifier is crucial; we discuss the features we define in
\Sref{sec:features}. We report our results in
\Sref{sec:results} and conclude with suggestions for future
research.

@@

\section{Model Overview}
%\label{sec:features}

\nss{I think we should break this up into sections by feature group (below). 
Here we can talk about learning and regularization and give a high-level overview 
of features.}

We define a large arsenal of features, our motivation being both to
improve the accuracy of classification and to be able to interpret the
characteristics of the language produced by speakers of different
L1s. In this section we define the features and motivate their use.%
\footnote{Whenever counts are mentioned, we use the log of the count
  as the feature.}  
While some of the features were used in the works surveyed in
\Sref{sec:literature}, many are novel, and are inspired by the
features used to identify translationese by \citet{vered:noam:shuly}.
We also report the accuracy of using each feature type, in isolation,
on the training set.

@@

\section{Main Features}\label{sec:mainfeats}

These four feature groups form the core of our model.

\subsection{\feat{POS}: part-of-speech sequences}

\subsection{\feat{FreqChar}: frequent character $n$-grams}

\subsection{\feat{CharPrompt}: character $n$-grams paired with the prompt ID}

\subsection{\feat{Brown}: Brown clusters}

\section{Additional Features}

Each of these adds a small number of parameters to the model. 
We report the empirical improvement that each of these brings 
independently when added to the main features (\Sref{sec:mainfeats}).
The full model combines all features.

\subsection{\feat{CxtFxn}: Contextual function words\nss{does this subsume pronouns?}}

\subsection{\feat{DocLen}: Document length in tokens}

\subsection{\feat{Misspell}: Spelling correction edits}

\subsection{\feat{Position}: \nss{?}}

\subsection{\feat{Pron}: pronouns\nss{?}}

\subsection{\feat{PsvRatio}: Ratio of passive to active voice verbs\nss{or is it the proportion of passive verbs?}}

\subsection{\feat{Punct}: Count of each punctuation mark}

\subsection{\feat{Restore}: LM-restored function words}

\subsection{Discarded Features}

\nss{things that didn't help in our preliminary experiments}
